\documentclass[12pt, a4paper]{article}
\addtolength{\oddsidemargin}{-.875in}
\addtolength{\evensidemargin}{-.875in}
\addtolength{\textwidth}{1.75in}
\addtolength{\topmargin}{-.875in}
\addtolength{\textheight}{1.75in}

\usepackage{indentfirst}
\usepackage{graphicx}

\begin{document}
\noindent
Nicholas Garrett\\ \\
Professor Dailami\\ \\
CS 3316\\ \\
9/30/2021\\ \\


\begin{center}
	\centering{	Homework 3\\ }
\end{center}

\noindent
1.\\
Computer science was not always what I wanted to pursue a career in.  Originally, I actually had been interested in volcanology and geology.  However, as I got older and computers became more and more a part of my life, the predictable logic they follow really drew me in.  It started with Arduino, a re-programmable micro-controller, being able to actually control something that would interact with the world, whether it be turning on a light or moving a rover was what got my attention. \\

 With code, I could actually control something and make it do whatever I wanted--programming code was logical.  From Arduino, I moved to the Raspberry Pi and Python, and from there my eyes were opened just a little bit wider to the expansive world of CS. \\

Just like what had been my first interests, the more I learned about opportunities available in computer science, the more I could know what I actually would find interesting.  From robotics, my interests have narrowed to cybersecurity.  I suppose the aspects of it that I find most interesting and attractive is the constant challenge of being a step ahead, and not two steps behind, those who are trying to take advantage of lax security.  Cybersecurity seems to be a sort of ``jack of all trades'' in computer science by its very nature; in order to properly defend a system, one must understand it as much as possible.  So, I will be able to learn as much as possible about systems.  \\

This is truly what I want, to be able to know and understand extensively the inner workings of computers--how to make the bend to my will, and how to keep that control from others.  I suppose that from that, my ideal job description would be something where I have opportunity to expand my knowledge and enhance my education, and doing the things that I enjoy. \\ \\ \\

\noindent
2.\\

.1.\\

Title: 

Cyber Security Officer \\

Description: 

Protect agency data and information using a variety of tools, packages, and software systems.\\

Company name: 

CIA (Central Intelligence Agency) \\

Company description: 

An intelligence service of the government of the united states.\\

Add Value?:

	I believe that I could add value to this position through my unique perspective of being of a younger generation than most cybersecurity analysts.  Cyber attacks are made by individuals of the generation of, or close to what I am a member of.  Thus, older and dated theories of security may not consider possibilities members of my general age group would think of to attack.\\ \\

.2.\\

Title: 

Security Consultant\\

Description: 

Provide support and direction to branches and teams in and of the company.  \\

Company name: 

Microsoft \\

Company description: 

A technology corporation that produces computers, electronics, and software services.\\

Add Value?:

	I can add value to this position through the emphasis my education has followed in cybersecurity.  The bachelor's degree in Computer Science and certificate in cybersecurity I will have completed would give me a strong basis and standing in the cybersecurity field. \\ \\
	
	
.3.\\

Title: 

IT Specialist\\

Description: 

Serve as an IT Specialist in the Enterprise Information Security Unit.\\

Company name: 

FBI (Federal Bureau of Investigation) \\

Company description: 

The domestic intelligence and security service of the United States.\\

Add Value?:

	I believe that I could add value to this position through my dedication to doing my best in a job.  If I don't know something that is asked, you can be sure that I will do my best to research that topic.  As a result, I will do my best to ensure that any ignorance or misinformation does not persist on my part.\\ \\ \\

\noindent
3.\\
 Internship and Externship are two terms often used interchangeably.  However, while they do mean close to the same thing, there are subtle differences between the two.\\
 
 An externship is something more closely resembling a job shadowing.  These typically last more than two weeks and less than a month.    
 
An internship allows individuals to gain experience through actually working on the job.  They can be paid or unpaid, like an externships, though are also longer in length, typically lasting more than a few weeks.

\end{document}  